Sulfur Dioxide on Water's Surface

### 2011-04-07 TransitOrientation.tex
Finishing up the 2nd draft. Added new so2/h2o molecule cartoons, and a cartoon for the molecular layout near the interface for both systems.
Incorporating Stephanie's comments from draft 2 and reworking the surface-location image

	From its starting position 20\angs~above the water surface, until the \suldiox~moves to within 10\angs~of the surface of both systems, the orientation is isotropic in $\theta$ and $\phi$. Near the surface the bisector angle $\theta$ becomes more perpendicular ($\cos(\theta)\approx1$) with the \suldiox~sulfur pointing into the water phase. At the point when the \suldiox~reaches the surface location (distance $=0$\angs), the bisector is perpendicular in both the neat-water and saturated systems. Figure \ref{fig:so2-surface-angles}a depicts \suldiox~near the water surface with the bisector aligned perpendicular to the interface. There are differences between the two systems as to where the point of transition from isotropic to preferred orientations happens. In the absence of simulated ionic species that form through \suldiox-\wat~chemistry at the surface, it is clear that the adsorbing \suldiox~in the gas phase takes on a preferred orientation to adsorb on a water surface.

@@

  % talk about phi differences
  With a mostly perpendicular bisector angle, it is expected that the values of $\phi$ would be isotropic relative to the reference axis. This is the case in both systems, with one exception in the neat-water system. At the neat-water surface and just below from 0\angs~to 5\angs~in the water phase, the $\theta$ profile broadens, and a clear trend appears in the profile of $\phi$. This corresponds to a \suldiox~orienting less flat to the surface (inclined up to 60 degrees from the surface normal). The result is that \suldiox~in this region shows a preference for one of the S-O bonds to point more towards the aqueous bulk and the other to point away towards the interface. Figure \ref{so2-surface-angles}b depicts the orientation of the \suldiox~slightly below the water surface. This is in contrast to \suldiox~molecules above the surface, oriented more perpendicularly. The behavior is likely due to the interaction between the waters and one of the S-O bonds leading to a higher solvation than above the water surface. As the \suldiox~is solvated by more highly-coordinate bulk water, the S-O bonds experience less equal interaction environments. Baer et al. noted that their force field model for the \suldiox~does not reproduce well the first hydration shell geometries,\cite{Baer2010} so conclusions regarding the specific interactions and hydrate geometries between the \suldiox~and \wat~cannot be made here. It is notable that the same reorientation does not occur as strongly in the saturated system. The presence of the adsorbed \suldiox~layer apparently decreases the reorienting behavior likely because of the disrupting effect the higher \suldiox~concentration has on the water interactions at the surface. Below this 5\angs~region under the surface, the \suldiox~resumes an isotropic orientation as it becomes fully solvated by bulk waters.

>>>>

	From its starting position 20\angs~above the water surface, until the \suldiox~moves to within 10\angs~of the surface of both systems, the orientation is isotropic in $\theta$ and $\phi$. Near the surface the bisector angle $\theta$ becomes more perpendicular ($\cos(\theta)\approx1$) with the \suldiox~sulfur pointing into the water phase. At the point when the \suldiox~reaches the surface location (distance $=0$\angs), the bisector is perpendicular in both the neat-water and saturated systems. Figure \ref{fig:so2-surface-angles}a depicts \suldiox~near the water surface with the bisector aligned perpendicular to the interface. In the absence of simulated ionic species that form through \suldiox-\wat~chemistry at the surface, it is clear that the adsorbing \suldiox~in the gas phase takes on a preferred orientation to adsorb on a water surface. The main difference between the two systems is where the point of the transition from isotropic to preferred orientations is found.

@@

  % talk about phi differences
  With a mostly perpendicular bisector angle, it is expected that the values of $\phi$ would be isotropic relative to the reference axis. This is the case in both systems, with one exception in the neat-water system. At the neat-water surface and just below, from 0\angs~to 5\angs~in the water phase, the $\theta$ profile broadens, and a clear trend appears in the profile of $\phi$. This corresponds to a \suldiox~orienting less flat to the surface (inclined up to 60 degrees from the surface normal). The result is that \suldiox~in this region shows a preference for one of the S-O bonds to point more towards the aqueous bulk and the other to point away towards the interface. Figure \ref{fig:so2-surface-angles}b depicts the orientation of the \suldiox~slightly below the water surface. This is in contrast to \suldiox~molecules above the surface, oriented more perpendicularly. The behavior is likely due to the interaction between the waters and one of the S-O bonds leading to a higher solvation than above the water surface. As the \suldiox~is solvated by more highly-coordinated bulk water, the S-O bonds experience less equal interaction environments. Baer et al. noted that their force field model for the \suldiox~does not reproduce well the first hydration shell geometries,\cite{Baer2010} so conclusions regarding the specific interactions and hydrate geometries between the \suldiox~and \wat~cannot be made here. It is notable that the same reorientation does not occur as strongly in the saturated system. The presence of the adsorbed \suldiox~layer apparently decreases the reorienting behavior likely because of the disrupting effect the higher \suldiox~concentration has on the water interactions at the surface. Below this 5\angs~region under the surface, the \suldiox~resumes an isotropic orientation as it becomes fully solvated by bulk waters.
